Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-10 manuscript/manuscript.Rmd
latex header

---
title: Categorical Predictor Embeddings in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevin@kasa.ai
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants
    email: ronaldrichman@gmail.com
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
output:
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
extra_dependencies: ["amsmath"]

@@

## Categorical data modeling

@@

>>>>

---
title: Categorical Predictor Embeddings in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevin@kasa.ai
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants
    email: ronaldrichman@gmail.com
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
output:
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
header-includes: |
    \usepackage{amsmath}
    \usepackage{mathtools}
    \DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

## Categorical data modeling {#catdata}

@@

Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions:
instead of mapping factor levels to real numbers, we map them to a point in Euclidean space, where the dimension of the space is the ceiling
of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$.
